\begin{center}
\section{HMM - TIDIGIT data}
\end{center}

\subsection{Introduction}
\begin{flushleft}
  HMM is a statistical model where we use supervised learning to create the model.
  The model contains hidden states. We attach state transition probability to each state.
  The states can emit symbols with certain probabilities. \break
  The state transition probabilities and 
  symbol emission probabilities are calculated using Baum Welch algorithm.
  The classification of a particular sequence is done using Vitterb algorithm on the constructed HMM.
\end{flushleft}

\subsection{Goal}
\begin{flushleft}
    Identify digit sequence from speech using HMM(Hidden Markov Model) using HTK tool kit.
\end{flushleft}

\subsection{Data}
\begin{flushleft}
  Given .mfcc files corresponding to diffenent digit sequence uttered by men and womnen.
  The .mfcc files contains the features extracted from .wav files.
  All the train and test data was already separated.
\end{flushleft}


\subsection{Observation and Preprocessing of Data}
\begin{flushleft}
    
  All given .mfcc files were containing around 400 feature vector with 38 component each.
  The fist line of .mfcc file was indicating the no of feature vector and number of components.

  We were about to use HTK toolkit to do the experiment.
  The following stepas were taken
  1. To use the HTK tool kit we need to convert the .mfcc files to .htk format. To do this we have used matlab script file.
  2. To use the matlab script we need to truncate the first line of the provided .mfcc files.
  3. To use the matlab script we also need a filelist file with all .mfcc file paths.
\end{flushleft}

\subsection{Experiment}
\begin{flushleft}
  We have HTK toolkit for the entire experiment.
  
  The steps taken as follows. \break
  
  1. Create grammer file \break
  \begin{lstlisting}[language=bash]
    $ HParse ... (i/p: grammer, o/p: wordnet)
  \end{lstlisting}
  2. Create {wlist} file \break
  
  3. Create {lexicon} file \break
  \begin{lstlisting}[language=bash]
    $ HDMan ... (i/p: wlist, lexicon, model0, o/p: dict, dlog)
 \end{lstlisting}
  4. Create {all.mlf} file. The all.mlf file contains all label for man and woman mfcc files \break
  
  5. Create {all.scp} file. This is the training scp file. The all.scp file contains all label for man and woman mfcc files \break
  
  6. Create {proto} file √ \break
  \begin{lstlisting}[language=bash]
    $ HCompV ... (i/p: all.scp, proto, o/p: newproto) \break 
  \end{lstlisting}
  
  7. Create {hmmdefs} file containg all HMMs for diffenent digits. hmmdefs was created by renaming the ~h option to digit name 
    inside the newproto created using \$ HCompV and make multiple copies for each digit in one hmmdefs.
    
  8. We created {macros} file using {vFloors} file
  
  \begin{lstlisting}[language=bash]
    $ HERest ... (i/p: macros, hmmdefs, o/p: newproto)
    \end{lstlisting}
    (repeat 4 or more times using previously generated proto)
    \break
    
    \begin{lstlisting}[language=bash]
    $ HHEd ... (i/p: macros, hmmdefs, o/p: newHmmdefs.mlf)
    \end{lstlisting}

    
    \begin{lstlisting}[language=bash]
    $ HResults ... (i/p: allTest.mlf, o/p: result.mlf, confusiton matrix)
    \end{lstlisting}
    
  In the above experiment we have tried using \break
    5 states and 1 mixture for each digit with efficiency \textbf{\textit{26\%}}. \break
    8 states and 1 mixture for each digit with efficiency \textbf{\textit{50\%}}. \break
    12 states and 1 mixture for each digit with efficiency \textbf{\textit{70\%}}. \break
    20 states and 1 mixture for each digit with efficiency \textbf{\textit{71\%}}. \break
    12 states and 5 mixture for each digit with efficiency \textbf{\textit{90\%}}. \break
\end{flushleft}

\subsection{Inferances}
\begin{flushleft}
  1. It was observed that with the increase of state number and mixture for each digit the effenciy increases.
\end{flushleft}

\subsection{Links}
\begin{flushleft}
  All the codes are available at the following
  \color{red} 
    \href{https://github.com/holasm/pr_assignment3/tree/master/hmm/tidigits/codes}{link}.
  \end 
  3c36055eb64e50119ca39c844605bf59b824cb43
\end{flushleft}